Generation of TypeScript Declaration Files from JavaScript Code

### 2021-05-26 mplr-2021/main.tex
related work

As a measure of the quality of a generated file we use its distance to
the declaration file provided for the same module on
DefinitelyTyped. In other words, we use DefinitelyTyped as our ground truth.
To this end, we created \texttt{dts-compare}, a tool to compute the
differences between two TypeScript declaration files.
% \begin{itemize}
%   \item \texttt{dts-parse}: A TypeScript declaration files parser, which transforms the file into a JSON file with a defined structure.
%   \item \texttt{dts-compare}: A tool that uses \texttt{dts-parse} and compares two TypeScript declaration files computing differences by applying several criteria.
% \end{itemize}

@@

\paragraph*{Further types}
Similar approaches could be conceived for indexed types, polymorphic types, dependent
types, etc. However, at present we believe incorporating these features in a tool to be
overblown because they are not widely used in DefinitelyTyped (see
Table~\ref{tab:dts-parse-stats}).

@@

>>>>

As a measure of the quality of a generated file we use its distance to
the declaration file provided for the same module on
DefinitelyTyped. In other words, we use DefinitelyTyped as our ground
truth, because it is the only available reference against we can
compare our results.
To this end, we created \texttt{dts-compare}, a tool to compute the
differences between two TypeScript declaration files.
% \begin{itemize}
%   \item \texttt{dts-parse}: A TypeScript declaration files parser, which transforms the file into a JSON file with a defined structure.
%   \item \texttt{dts-compare}: A tool that uses \texttt{dts-parse} and compares two TypeScript declaration files computing differences by applying several criteria.
% \end{itemize}

@@

\paragraph*{Further types}
Similar approaches could be conceived for indexed types, polymorphic types, dependent
types, etc. However, at present we believe incorporating these
features in a tool to be of limited value because they are not widely used in DefinitelyTyped (see
Table~\ref{tab:dts-parse-stats}).

@@

\paragraph{Data Type Inference}
Petricek and coworkers describe a mechanism to infer a datatype from
an example input in JSON, XML, or CSV format
\cite{DBLP:conf/pldi/PetricekGS16}. Their implementation relies on
type providers, a metaprogramming facility of F\#. The type provider reads the
example input at compile time and translates it into a static
type. The approach is purely data-centric---the shape of the sample
data determines what is legal in the program. Our approach
analyzes the program's behavior on sample data and generalizes these
observations to a type.
